---
title: "R Fibonacci Solution"
author: "Sydney Bolim Son"
date: "4/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# What is the *n*th number in the Fibonacci sequence?

The Fibonacci sequence is a sequence of numbers in which each number is the sum of the previous two numers. The sequence begins with 0 and 1. It is defined as $$F_n = F_{n-1} + F_{n-2}$$ where $F_0 = 0$ and $F_1 = 1$.

For example, here is the sequence through the 12th number.For example, here is the sequence through the 12th number.

| $F_0$ | $F_1$ | $F_2$ | $F_3$ | $F_4$ | $F_5$ | $F_6$ | $F_7$ | $F_8$ | $F_9$ | $F_{10}$ |$F_{11}$| $F_{12}$ |
| :-----------: | :-----------: | :-----------: | :-----------: | :-----------: | :-----------: | :-----------: | :-----------: | :-----------: | :-----------: | :------------: | :------------: | :------------: |
|       0       |       1       |       1       |       2       |       3       |       5       |       8       |      12       |      21       |      34       |       55       |       89       |      144       |

Write a R program to print out the *n*th number in the sequence. 

For example, `fib(10)` should give an output `55`.

For a greater challenge, optimize the above solution to improve runtime complexity. 


## __Method 1: `for` loop__

```{r}
start_time <- Sys.time()
# for loop
n <- 10

len <- n
fibvals <- numeric(len)
fibvals[1] <- 1
fibvals[2] <- 1
for (i in 3:len) { 
   fibvals[i] <- fibvals[i-1]+fibvals[i-2]
} 
end_time <- Sys.time()

# To get the nth fibonacci number change the n above in the loop
fibvals[n]

# Peformance of the loop is
end_time - start_time
```


## __Method 2: Recursion__

```{r}
fibonacci <- function(n){
  if (n<0){
    print("Please stick to positive numbers fo now")
  } else if (n==0){
    return(0)
  } else if (n==1){
    return(1)
  } else{
    return(fibonacci(n-1)+fibonacci(n-2))
  }
}
```

```{r}
fibonacci(10)
```

```{r}
start_time <- Sys.time()
fibonacci(10)
end_time <- Sys.time()

end_time - start_time
```



## __Method 3: Recursion & List Indexing__

```{r}
memoize_me_capn <- list()

fibonacci_2 <- function(n){
  if (n<0){
    print("Please stick to positive numbers fo now")
  } else if (n==0){
    value <- 0
  } else if (n==1){
    value <- 1
  } else{
    value <- fibonacci_2(n-1)+fibonacci_2(n-2)
  }
  memoize_me_capn[n+1] <- value
  return(value)
}
```

```{r}
fibonacci_2(10)
```

```{r}
start_time <- Sys.time()
fibonacci_2(10)
end_time <- Sys.time()

end_time - start_time
```
